Dismal Code: Studying the Evolution of Security Bugs

### 2013-06-21 docs/evol.tex
work on the reviewers comments

Initially, we obtained a snapshot (January 2012) of the Maven repository and
handled it locally to retrieve a list of all the names of the project versions
that existed in it. A project version can be uniquely identified by the triplet:
{\it group id}, {\it artifact id} and {\it version}.
Since FindBugs analyses applications written in the Java
programming language, and the Maven repository
hosts projects from languages other than Java such as Scala, Groovy,
Clojure etc. we filtered out such projects by performing a series of checks in
the repository data and metadata.

>>>>

Initially, we obtained a snapshot (January 2012) of the Maven repository and
handled it locally to retrieve a list of all the names of the project versions
that existed in it. A project version can be uniquely identified by the triplet:
{\it group id}, {\it artifact id} and {\it version}.

FindBugs is an open source static analysis tool that
searches for software bugs. It works by examining the compiled Java virtual
machine bytecodes of the programs it checks, using the bytecode engineering
library ({\sc bcel}).
To detect a bug, FindBugs uses various formal methods like
{\it control flow} and {\it data flow
analysis}. It has also other detectors that employ {\it visitor patterns} over
classes and methods by using {\it state machines} to reason about values stored
in variables or on the stack.
Since FindBugs analyses applications written in the Java
programming language, and the Maven repository
hosts projects from languages other than Java such as Scala, Groovy,
Clojure etc. we filtered out such projects by performing a series of checks in
the repository data and metadata.
